\documentclass{article}

\begin{document}
	\begin{center}
	 \textbf{{JATIYA KABI KAZI NAZRUL ISLAM UNIVERSITY, TRISHAL}} \\
	 \vspace{2mm}
	 \textbf{ TRISHAL, MYMENSINGH} \\
	 \vspace{2mm}
	\textbf{{Department of Computer Science and Engineering}} \\
	
		
	
	\end{center}
	\vspace{25mm}
	\huge\textbf{{Submitted By :}}\\
	\large{Kanis Fatema  \\ Roll: 17102010\\ Session: 2016-17 \\ \\	                                                            
	Monisha Dey\\Roll: 17102032\\Session: 2016-17}\\\\
	\vspace{20mm}
		\begin{flushright}
	\huge\textbf{{Submitted To :}}\\
	\large{Dr.Selim Al Mamun  \\ Associate Professor\\Department of Computer Science and Engineering }\\
	\end{flushright}
\vspace{25mm}


\textbf{{Project Title: " THE WAY OF FUN: QUIZE" }}\\\\

\begin{center}
	\textbf{{Submission Date : 17 December,2018}} \\
	
\end{center}
\vspace{55mm}
	\huge\textbf{{Objective:}}
	
	
	\large{We want to do a project on Quiz Game. Here we want to add three levels. All the levels will contain 5 questions. }	\\\\
	\huge\textbf{{Motivation of this game:}}

	\large{We eagerly want to work on a project as titled Quiz Game. Here we will able to play three levels. Each level will contain 5 questions. For each right answer the player will gain 5 pints for the first level, in the second level there will be add 10 points, in the third level there will add 20 points. We will use the programming language JAVA and NetBeans IDE to compile our program code.}\\\\
	\huge\textbf{{Introduction: }}

	\large{We will start the program by showing screen to the user where it will show the name of the game. Then there will be an input screen where the game will require the country of the player and the name of the player. Then another input screen will come and there will be asked about which level the player wants to play. The level will be like easy, medium and hard. }\\\\
	\huge\textbf{{Background state of the problem:}}
	
	\large{We have learned java language to do the project. We also have the knowledge about the compilers which are NetBeans IDE and.We also read the book of Herbert Schildt and Balagurusamy to know more about java language. 
	 }\\\\
	\huge\textbf{{Methodology/ experimental design:}}\\
	\large{After run the project we see 3 option:\\
		Easy\\ 
		Normal\\ 
		Hard\\
		Then we have to select one option 
		1.We will start the program by showing screen to the user where it will show the name of the game. 
		2.Then there will be an input screen where the game will require the country of the player and the name of the player. 
		3.Then another input screen will come and there will be asked about which level the player wants to play. The level will be like easy, medium and hard. 
		4. In the easy level there will be 5 five easy questions which is very easy to answer, in the medium level there will be more harder, in the hard level there will be very hard questions.
		}\\\\
	\huge\textbf{{Conclusion:}}
	
	\large{If we successfully complete this project then it will be very much helpful and enjoyable game for all of us.there will be many general knowledge related questions which will enlarge our IQ. Overall,  this game will improve our proficiency. }
	
\end{document}